\documentclass[10pt]{article}

\usepackage{charter}
\usepackage{fullpage}
\usepackage[numbers]{natbib}
%\usepackage[resetlabels]{multibib}
\usepackage[ManyBibs]{currvita}
\usepackage{url}


%\newcites{journal,conference,poster,workshop,position,other}{Journal,Conference,Poster,Workshop,Position,Other}
%\newcites{refpaper}{foo}
%\newcites{unrefpaper}{foo}
%\newcites{journal}{foo}
%\newcites{techreport}{foo}
%\newcites{submitpaper}{foo}
%\newcites{classproject}{foo}


% Better for lists with 1-2 items and short descriptions
\newenvironment{sublist}{%
	\begin{list}{}{%
		\setlength{\itemsep}{0em}\setlength{\parsep}{0em}%
		\setlength{\topsep}{0em}\setlength{\parskip}{0em}%
	}%
}%
{ \end{list} }

% Better for lists with more than 2 items and/or long descriptions
\newenvironment{subbulletlist}{%
	\begin{list}{\labelitemii}{%
		\setlength{\topsep}{\itemsep}\setlength{\parskip}{\parsep}%
	}%
}%
{ \end{list} }

\begin{document}
% This is what will appear at the very top of your CV.
\begin{cv}{Tony Kovanen\\{\large \itshape Curriculum Vitae}}
%\date{}

\begin{cvlist}{Contact}
	\item
	Hevosmiehenkatu 13 F 67\\
	00770 Helsinki\\
	Finland
	\item Mobile: +358400904910
	\item E-mail: tony.kovanen@gmail.com
\end{cvlist}


\begin{cvlist}{Personal Information}
	\item Date of Birth: 2 September 1991\\
		Place of Birth: Helsinki, Finland\\
		Citizenship: Finnish\\
        Languages Known: Finnish (native speaker), English (excellent), Spanish (basics), German (basics), Swedish (basics).
\end{cvlist}

\begin{cvlist}{Education}
	\item \emph{{\bf B.Sc. Student}, Computer Science}, September 2011 - till date\\
	University of Helsinki, Finland
	% Sublists don't have any extra vertial space.
	\begin{sublist}
	\item B.Sc. Thesis: \textit{Analysis of Test Coverage with Mutation Analysis} (graded, 5/5)
	\item Advisor: Dr. Matti Luukkainen
        \item M.Sc. Thesis: \textit{Organizing View Structures: What Can We Learn From the Web?} (starting)
        \item Advisor: Matti Luukkainen
        \item GPA: 5/5 (till date)
        \item ECTS credits: 317 (till date)
	\end{sublist}
\end{cvlist}

\newpage
\begin{cvlist}{Employment}
	\item[6/2012--5/2014] {\bf Research Assistant}\\
	Helsinki Institute for Information Technology HIIT\\
	Department of Computer Science\\
	University of Helsinki, Finland
	\item[6/2014--till date] {\bf JavaScript Wrangler}\\
	Automattic, Inc.
\end{cvlist}

\begin{cvlist}{Research Visits}
	\item[9/2010--10/2012] {\bf German Research Center for Artificial Intelligence, DFKI}\\		
		Innovative Retail Laboratory\\	
		Topic: Augmented reality assisted indoor navigation
\end{cvlist}

\begin{cvlist}{Conference Appearances}
	\item[Nodefest JP 2014]      {\bf Real-time communication with Socket.IO 1.0}\\
	\item[JSConf AR 2014] {\bf WordPress, JavaScript, Node.JS and you}\\
\end{cvlist}

\begin{cvlist}{Open Source Contributions}
	\item \textbf{TMC - Test My Code}\\
    An extension to a system for automatically assessing and scoring programs written by students in an IDE to support C/C++ languages. 
	\item Project website: \url{https://github.com/testmycode}	

	\item \textbf{Socket.IO}\\
    Core team member of Socket.IO, a framework for bidirectional real-time communication with great backwards compatibility support. Working closely in Socket.IO and underlying modules with a focus on lower level communication (Engine.IO). Author of binary support in Engine.IO.
	\item Project website: \url{http://socket.io}	

	\item \textbf{Zuul}\\
    One of the maintainers of Zuul, a browser based testing solution that provides multi-browser test environments through cloud services.
	\item Project website: \url{http://github.com/defunctzombie/zuul}	

	\item \textbf{Superagent}\\
    One of the maintainers of Superagent, an AJAX library that provides a similar builder pattern based API both on Node.JS and the browser.
	\item Project website: \url{http://visionmedia.github.io/superagent/}	

	\item \textbf{Jetpack}\\
    Team member in Jetpack, a WordPress plugin bringing your favorite WordPress.com features to your self-hosted WordPress installation.
    	\item Project website: \url{http://jetpack.me}	
\end{cvlist}

\newpage % currently best for formatting
\begin{cvlist}{Special Skills}
\item JavaScript, Node.JS, Socket.IO, Express, React, BackboneJS, PHP, WordPress, Java, Ruby, Ruby on Rails, C, C++, Matlab, Android, PostgreSQL, Git, CSS (working knowledge), Spring Web MVC (basics), OpenCV (basics), OpenGL (basics). 
\end{cvlist}

\begin{cvlist}{Teaching}
	\item {\bf Course Instructor}\\
    Programming Project (Java)\\
    Database Application\\
    Programming project: AI Odyssey
		
	\item {\bf Teaching Assistant}\\
	Methods for Software Engineering\\
    Data Structures and Algorithms\\
    Programming in C\\
    Location-Awareness\\
    Node.JS Programming Project\\

	
	For more information see the University employee page: \url{http://www.cs.helsinki.fi/en/people/tonykova}
\end{cvlist}	
\end{cv}
\end{document}



